Quality Metrics for SKOS Vocabularies

### 2012-03-11 introduction.tex
updated abstract + intro

% What is SKOS?

The Simple Knowledge Organization System (SKOS) \todo{CM}{reference, no footnote} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.

% What does "quality" mean in this context?

Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply some guidelines or rules (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-complete suggestions.

@@

	\item The SKOS version of Agrovoc defines concepts in 25 different languages. However, almost all concepts have an English description, 38\% of all concepts don’t have German labels attached. This can be a problem for applications that use Agrovoc and rely on German translations.

	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels. As a result, the auto-complete function of the online search interface suggested identical entries, with no disambiguation information.

	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}), which contains 11 disconnected concept clusters. Confronting the thesaurus maintainers with these structures, they recognized them as “forgotten” test data that has no practical significance.

@@

% How can we improve quality?

%When a machine agent finds a vocabulary on the Web, it can check whether or not a vocabulary fulfills the low-level integrity conditions demanded by the SKOS specification. However, these
One reason for these quality problems is that SKOS currently only defines a set of \textbf{low-level integrity conditions}, which, when being enforced, ensure the structural and semantic requirements of the SKOS specifications but fail to capture \textbf{higher-level quality issues}, as those mentioned in the examples before. Another problem is that existing vocabulary design guidelines and best practices purely rely on \textbf{human assessment}, which is highly subjective and doesn’t scale when vocabulary quality assessment should be performed on larger, possibly linked Web vocabularies.

We believe, and recent developments of quality checking tools (e.g., PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}}, qSKOS\footnote{\url{https://github.com/cmader/qSKOS}}, SKOSify\footnote{\url{http://code.google.com/p/skosify/}}) support this motivation. This, however, requires a formalization of the notion of quality with respect to SKOS vocabularies, which can be used in order to consistently implement quality assessment procedures across tools. Since, the notion of “quality” with respect to SKOS vocabularies naturally varies across application domains it is hard, if not impossible, to come up with a general definition of quality. However, we believe that vocabulary designers can apply a set of \textbf{formal quality criteria} on given vocabularies in order to assess whether or not a vocabulary fulfills their requirements. Since these criteria are based on a formal definition, they can be calculated by automated tools, which helps vocabulary designers in assessing the quality of available or newly created vocabularies and provide important feedback to the overall vocabulary design process.

The main contributions of this work can be summarized as follows:
\begin{itemize}
	\item We derived a \textbf{quality criteria catalogue} from existing literature, tools, and public mailing list discussions in the community. We \textbf{formalized} each criterion and implemented them in the \textbf{qSKOS quality assessment tool}.

	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.
\end{itemize}

The results from our studies show that... TBD

>>>>

% BACKGROUND

% What is SKOS?
The Simple Knowledge Organization System (SKOS) \todo{CM}{reference, no footnote} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} have created SKOS representations of their controlled vocabularies and published them on the Web so that they can easily be accessed and by humans and machines.

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and vocabulary designers usually apply their own guidelines and rules (cf.,~\cite{Coronado2009}\todo{CM}{is this correct?}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

	\item The SKOS representation of Agrovoc defines concepts in 25 different languages. However, while most concepts have an English description, only 38\% of all concepts have German labels attached. This can be a problem for applications that use Agrovoc and rely on German translations.

	\item The previous version of the STW thesaurus, contained 5 pairs of concepts with identical labels. As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.

% Note: examples related to "defense / army & co" are always a bit tricky; maybe we find a better example.

	\item The vocabulary developed by the Austrian Armed Forces (LVAk thesaurus\footnote{Non-public thesaurus developed by the Austrian Armed Forces}) contains 11 disconnected concept clusters. When we confronted the thesaurus maintainers with these structures, they recognized them as ``forgotten'' test data that has no practical significance.

% Note: I am still having problems to imagine why and how one would implement query expansion based on the DBPedia categories...as long as this is not clear, better skip the example.

@@

% PROBLEM / RESEARCH QUESTION

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}]. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions. However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model. Such criteria might be part of design rules and guidelines, but rely on \textbf{human assessment}, which is highly subjective and doesn’t scale for larger, possibly linked Web vocabularies.

% CONTRIBUTION

The goal of our work is to identify possible quality criteria for controlled vocabularies and to provide a set of quantitative quality indicators for SKOS vocabularies. We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

	\item We identified \textbf{quality criteria} for controlled vocabularies by examing existing literature, tools, and public mailing list discussions.

	\item We \textbf{formalized} them into computable \textbf{quality metrics} and implemented them in the \textbf{qSKOS quality assessment tool}.

	\item We \textbf{analyzed} a representative \textbf{set of existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.

The results from our studies show that... \todo{BH,CM}{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

### 2012-03-11 main.tex
updated abstract + intro

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies. We identified existing \textbf{quality criteria} and formalized them into computable quality metrics. We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies. Our results indicate that \todo{CM,BH}{summarize results in one sentence}.

>>>>

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support domain experts with quantitative indicators to judge the quality of SKOS vocabularies. We identified existing \textbf{quality criteria} and formalized them into computable \textbf{quality metrics}. We implemented them in the qSKOS quality assessment tool and used it to analyze the quality of existing vocabularies. The results from this analysis indicate that \todo{CM,BH}{summarize results in one sentence}.
